Drake Plan

### 2020-01-03 R/drake_plan_conus.Rmd
2017, allows varying reporting days for T/A

# Parameters ####
# the aer site info. file:
aer_stn_path = "/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/aeronet_locations_v3.txt"
# aer_data_path = '~/qnap_geo/aeronet/All_Sites_Times_All_Points_AOD20_20180603.dat'
# aer_data_path = '/scratch/temp/All_Sites_Times_All_Points_AOD20_20180603.dat' 
# the aer data files:
aer_files_path = "/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/ALL_POINTS/"
date_start = "2018-01-01" # do not include in sel_data_bytime if don't want to limit
date_end   = "2018-12-31" # do not include in sel_data_bytime if don't want to limit
sats = c("terra", "aqua")

# MCD19 data load and save output: 
mcd19path = "/data-coco/mcd19/fst/nemia/2018/" # now there is only 2018 data 
mcd19path_CONUS = "/data-coco/mcd19/fst/conus/2018/"
MCD19_T_files <- list.files(path = mcd19path_CONUS, pattern = "T", full.names = T)
MCD19_A_files <- list.files(path = mcd19path_CONUS, pattern = "A", full.names = T)
out_dir = "/data-coco/mcd19/fst/conus/2018_AOD_newVar/"
# how many MCD days (files) to work on:
MCD_files_i = c(1:length(MCD19_T_files))

>>>>

# Parameters ####
this_year = 2017
# the aer site info. file:
aer_stn_path = "/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/aeronet_locations_v3.txt"
# aer_data_path = '~/qnap_geo/aeronet/All_Sites_Times_All_Points_AOD20_20180603.dat'
# aer_data_path = '/scratch/temp/All_Sites_Times_All_Points_AOD20_20180603.dat' 
# the aer data files:
aer_files_path = "/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/ALL_POINTS/"
date_start = "2017-01-01" # do not include in sel_data_bytime if don't want to limit
date_end   = "2017-12-31" # do not include in sel_data_bytime if don't want to limit
sats = c("terra", "aqua")

# MCD19 data load and save output: 
mcd19path = paste0("/data-coco/mcd19/fst/nemia/", this_year, "/")
mcd19path_CONUS = paste0("/data-coco/mcd19/fst/conus/", this_year, "/")
MCD19_T_files <- list.files(path = mcd19path_CONUS, pattern = "T", full.names = T)
MCD19_A_files <- list.files(path = mcd19path_CONUS, pattern = "A", full.names = T)
out_dir = paste0("/data-coco/mcd19/fst/conus/", this_year, "_AOD_newVar/")
if(!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)
# how many MCD days (files) to work on:
maxdays = as.integer(format(as.Date(paste0(this_year, "-12-31")), "%j"))
MCD_files_i = c(1:maxdays)
